Adaptive Sequential Model Selection

### 2015-07-23 paper.tex
rob

Given data $(y_i, x_{i1}, x_{i2},\ldots x_{ip})$ for $i=1,2,\ldots N$,
we choose a splitting  variable $j_1$ and split point $t_1$, leading to a model of the form
\begin{eqnarray}
\hat y_i=\beta_0 +\beta_{11} I(x_{ij_1} \leq t_1) +\beta_{12} I(x_{ij_1} > t_1)
\end{eqnarray}
Then at the second stage, we try splitting one of the two daughter nodes, and choose the split and most reduces the residual sum of squares.
Suppose that a split of the first node is chosen, using predictor $j_2$ at split point $t_2$.  This leads to the interaction model of the form
\begin{eqnarray}
\hat y_i=\beta_0 +\beta_{11} I(x_{ij_1} \leq t_1) \cdot \beta_{31} I(x_{ij_2} \leq t_2)+   \beta_{11} I(x_{ij_1} \leq t_1) \cdot  \beta_{31} I(x_{ij_2} > t_2)  +\beta_{12} I(x_{ij_1} > t_1).\cr
\label{eqn:intmodel}
\end{eqnarray}
Note that the search for possible split points can be expressed through an exhaustive set of basis functions $I(x_{ij} \leq  t_i), (x_{ij}  > t_i)$ for each $t_i \in (x_{1j}, x_{2j}, \ldots x_{nj})$.
The procedure is somewhat similar to foreward stepwise regression, but with differences.
For example the set of candidate basis functions available at each stage are a function of what has been  previously entered into the model
Nonetheless,  the selection procedure  for the first set of $k$ splits can be expressed in polyhedral from $Ay \leq b$, and the saturated and selective inference procedures can be applied.
As before, the saturated p-values have an explicit truncated Gaussian form, while computation of the selective p-values require accept-reject sampling.

>>>>

Given data $(y_i, x_{i1}, x_{i2},\ldots x_{ip})$ for $i=1,2,\ldots N$,
we choose a splitting  variable $j_1$ and split point $t_1$, leading to a model of the form
\begin{eqnarray}
\hat y_i=\beta_0 +\beta_{11} I(x_{ij_1} \leq t_1) +\beta_{12} I(x_{ij_1} > t_1)
\end{eqnarray}
Then at the second stage, we try splitting one of the two daughter nodes, and choose the split and most reduces the residual sum of squares.
Suppose that a split of the first node is chosen, using predictor $j_2$ at split point $t_2$.  This leads to the interaction model of the form
\begin{eqnarray}
\hat y_i=\beta_0 +\beta_{11} I(x_{ij_1} \leq t_1) \cdot \beta_{31} I(x_{ij_2} \leq t_2)+   \beta_{11} I(x_{ij_1} \leq t_1) \cdot  \beta_{31} I(x_{ij_2} > t_2)  +\beta_{12} I(x_{ij_1} > t_1).\cr
\label{eqn:intmodel}
\end{eqnarray}
Note that the search for possible split points can be expressed through an exhaustive set of basis functions $I(x_{ij} \leq  t_i), I(x_{ij}  > t_i)$ for each $t_i \in (x_{1j}, x_{2j}, \ldots x_{nj})$.
The procedure is somewhat similar to foreward stepwise regression, but with differences.
For example the set of candidate basis functions available at each stage are a function of what has been  previously entered into the model
Nonetheless,  the selection procedure  for the first set of $k$ splits can be expressed in polyhedral from $Ay \leq b$, and the saturated and selective inference procedures can be applied.
As before, the saturated p-values have an explicit truncated Gaussian form, while computation of the selective p-values require accept-reject sampling.
